---
title: "Predict raised for projects using log"
author: "Jaymeen Gandhi"
date: "5/25/2020"
output: word_document
---

```{r}
require(tidyverse)
```

```{r}
require(modelr)
```


```{r}
projects = read_csv('C:/Users/jayme/Downloads/projects.csv')
projects
```

```{r}
f=raised ~ backers + duration
model = lm(f,data = projects)
summary(model)
```



## We will be predicting the raised variable based upon other variables.
## Since if we plot the raised variable graph it is positively scewed so we transform it to log.

```{r}
projects_l = projects %>% mutate(log_raised=log(raised))
projects_l
```

##Since we need to get rid of infinities we filter out projects greater than 1.

```{r}
projects = projects %>% filter(raised > 1)
projects1 =projects %>% mutate(log_raised = log(raised))
projects1
```


```{r}
f1 = log_raised ~ backers + duration
model_l = lm(f1, data = projects1)
summary(model_l)
```

```{r}
predictions = predict(model_l , data =projects1)
projects %>% mutate(predictions = predictions)
#exp(predictions)

projects2=projects %>% mutate(predictions = exp(predictions))
projects2

```


##Now let us understand the difference why to use log. So lets consider we are nor using any log.
## creating a new model for comparision 
##Creating a model without any log
```{r}
f = raised ~ duration
model_without_log = lm(f, data = projects)
summary(model_without_log)
predictions = predict(model_without_log,data = projects)
project3=projects %>% mutate(predict = predictions,err=predict-raised) 
project3
project3 %>% summarise(rmse = sqrt(mean(err^2)),rrmse = sqrt(mean(err^2/raised)))
```

##We can classify that, based upon the rmse values(error values) of normal model and the another of the log model.

```{r}
projects4 = projects %>% mutate(log_raised=log(raised))

f1<-log_raised~ duration

model_with_log=lm(f1, data=projects4)
summary(model_with_log)
l_predictions=predict(model_with_log, projects4)
predictions=exp(l_predictions)

projects4 =projects%>%mutate(predict=predictions, err=predict-raised)
projects4%>%summarise(rmse=sqrt(mean(err^2)) , rrmse=sqrt(mean((err/raised)^2)))
```



##Transforming the input variable.

```{r}
f4= raised ~ goal
model2 = lm(f4,data = projects)
summary(model2)
rmse(model2,data =projects )
```

```{r}
f5 = raised ~ sqrt(goal)
model3 = lm(f5,data = projects)
summary(model3)
rmse(model3,data = projects)
```